\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}

\title{Snapshot Objectives\\FlightSound}
\author{Group 05}
\date{May 15, 2026}

\begin{document}

\maketitle
\newpage

\tableofcontents
\newpage

\section{Snapshot 1 Objectives}

Snapshot 1 focuses on project planning, initial system setup, and foundational development for FlightSound.

\subsection{Project Planning}
\begin{itemize}
\item Finalize the project idea and overall system goals.
\item Create the Software Requirements Specification (SRS).
\item Create the initial Software Design Document (SDD).
\item Set up the Jira project board for sprint planning and task management.
\item Create the GitHub repository and establish the project workflow.
\end{itemize}

\subsection{Frontend Foundation}
\begin{itemize}
\item Create the main HTML, CSS, and JavaScript project structure.
\item Integrate the Google Maps JavaScript API.
\item Create the navigation bar and airport search interface.
\item Display a default airport map view centered on LAX.
\item Implement responsive page layout using Bootstrap 5.
\end{itemize}

\subsection{Backend Foundation}
\begin{itemize}
\item Set up the Java backend server running on port 8080.
\item Create the initial API endpoint structure.
\item Configure HTTP request handling using Java HttpServer.
\item Connect to the FlightLabs API for retrieving live flight data.
\item Create initial JSON parsing using Gson.
\end{itemize}

\subsection{Database Setup}
\begin{itemize}
\item Configure the SQLite database environment.
\item Create the users and preferences database tables.
\item Establish JDBC database connectivity.
\end{itemize}

\subsection{Docker Environment}
\begin{itemize}
\item Create Dockerfiles for frontend and backend containers.
\item Configure docker-compose.yml for multi-container deployment.
\item Verify that frontend and backend containers communicate successfully.
\end{itemize}

\newpage

\section{Snapshot 2 Objectives}

Snapshot 2 focuses on implementing the core functionality of FlightSound and beginning testing.

\subsection{Flight Data Features}
\begin{itemize}
\item Display real-time aircraft markers on the map.
\item Fetch nearby flight data based on airport selection.
\item Update aircraft positions dynamically from API responses.
\item Display aircraft information inside the side panel.
\end{itemize}

\subsection{Noise Visualization}
\begin{itemize}
\item Implement noise estimation calculations using altitude and aircraft type.
\item Create color-coded noise circles for aircraft markers.
\item Add a noise legend explaining low, medium, and high noise zones.
\item Implement noise overlay toggle controls.
\end{itemize}

\subsection{Weather Integration}
\begin{itemize}
\item Connect the backend to the Open-Meteo API.
\item Display temperature, wind speed, humidity, and weather conditions.
\item Link airport coordinates to weather requests.
\end{itemize}

\subsection{Authentication}
\begin{itemize}
\item Implement Google OAuth sign-in using Google Identity Services.
\item Create backend authentication endpoints.
\item Store authenticated user information in the SQLite database.
\item Maintain user session data using browser localStorage.
\end{itemize}

\subsection{Testing}
\begin{itemize}
\item Begin backend API endpoint testing.
\item Test frontend map rendering and marker updates.
\item Create Snapshot 2 TestRail reports.
\item Fix major bugs identified during testing.
\end{itemize}

\newpage

\section{Snapshot 3 Objectives}

Snapshot 3 focuses on feature completion, user preferences, integration testing, and UI improvements.

\subsection{User Preferences}
\begin{itemize}
\item Allow users to save a preferred airport.
\item Allow users to save a preferred address.
\item Implement geocoding for saved addresses.
\item Retrieve saved preferences on sign-in.
\item Add support for multiple noise calculation modes.
\end{itemize}

\subsection{User Interface Improvements}
\begin{itemize}
\item Improve the visual design of the map and side panels.
\item Improve responsive behavior for mobile and tablet devices.
\item Add loading indicators and error messages.
\item Improve navigation and overall usability.
\end{itemize}

\subsection{Help and Documentation Features}
\begin{itemize}
\item Create the Help page and FAQ section.
\item Explain aircraft noise calculations and map controls.
\item Add user guidance for airport search and preferences.
\end{itemize}

\subsection{System Integration}
\begin{itemize}
\item Fully integrate frontend, backend, database, and APIs.
\item Verify Docker container deployment works correctly.
\item Test communication between all services.
\item Optimize API response handling and database operations.
\end{itemize}

\subsection{Testing}
\begin{itemize}
\item Perform integration testing across all system components.
\item Conduct user interface testing.
\item Expand backend and frontend test coverage.
\item Generate Snapshot 3 TestRail reports.
\end{itemize}

\newpage

\section{Snapshot 4 Objectives}

Snapshot 4 focuses on finalization, deployment readiness, documentation completion, and final testing.

\subsection{Final System Improvements}
\begin{itemize}
\item Optimize application performance and API usage.
\item Resolve remaining bugs and stability issues.
\item Improve frontend responsiveness and map rendering speed.
\item Finalize database queries and backend logic.
\end{itemize}

\subsection{Deployment and Docker}
\begin{itemize}
\item Finalize Docker deployment configuration.
\item Verify production container compatibility.
\item Configure required environment variables for deployment.
\item Perform final deployment testing.
\end{itemize}

\subsection{Documentation}
\begin{itemize}
\item Finalize the SRS and SDD documents.
\item Complete the README and user manual.
\item Finalize the Design Specification document.
\item Update all version history sections.
\item Prepare the workflow diagram and architecture overview.
\end{itemize}

\subsection{Final Testing}
\begin{itemize}
\item Conduct full system testing and user acceptance testing.
\item Verify all API endpoints and frontend functionality.
\item Perform final authentication and database tests.
\item Generate Snapshot 4 TestRail reports.
\item Validate all project requirements have been completed.
\end{itemize}

\subsection{Project Submission}
\begin{itemize}
\item Prepare the final project presentation and demo.
\item Submit all source code, Docker files, and documentation.
\item Ensure the GitHub repository is fully updated.
\item Verify Jira sprint completion and documentation.
\end{itemize}

\end{document}